Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-11 manuscript.Rmd
Updated stuff.

df.96.10 <- df.96.10 %>% mutate(countNotCited = HD.N - (HD.N * propNotCited))

@@

@@

uncited.df <- rbind(df.96.10.Summary, df.95.11) %>%
    arrange(Year)
uncited.df$percentage <- uncited.df$Uncited/uncited.df$Published*100

uncited.df <- left_join(uncited.df, journals.year, by = "Year")

uncited.melted <- reshape2::melt(uncited.df[,c("Year", "Published", "Uncited", "N.Journals")], id.vars = c("Year", "N.Journals"))

@@

ggplot(uncited.melted, aes(Year, value, colour = variable,)) + 
    geom_line(alpha = .60) + 
    geom_point(size = 4) +
    scale_color_manual(values=cp, labels = c("Number of Articles Published",
         "Estimated Number of Uncited Articles")) +
    theme(legend.title=element_blank()) +
    theme(legend.position = "bottom") +
    ylab("N") +
    geom_text(data = percent.df, aes(Year, Uncited -70, label = percentLabel), size =4, colour = "black") +
    scale_y_continuous(breaks = seq(0, 2250, 250), limits = c(0, 2250))

@@

```{r plotArticleCount, eval=TRUE}
n.articles.year <- filter(full.df, attributes == "pubYear") 
year.split <- split(n.articles.year, n.articles.year$record)
year.count <- unlist(lapply(year.split, nrow))
year.count <- year.count[order(names(year.count))]
years <- names(year.count)

articles.year.df <- data.frame(years, year.count)
rownames(articles.year.df) <- NULL

#Annotation data file
articles.x <- as.factor(articles.year.df[c(1, 6, 12, 18, 25), 1]) 
articles.y <- articles.year.df[c(1, 6, 12, 18, 25), 2] 
articles.label <- as.character(articles.y)
articles.placement <- articles.y-50

plot.article.count <- ggplot(nsf, aes(as.factor(years), 
    y = n.grads, group=1)) + 
    geom_line(colour="red") + 
    geom_point(colour="red") + 
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    ggtitle("A. Number of Articles by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    ylim(c(0,2200)) + 
    geom_line(data = articles.year.df, aes(as.factor(years), y = year.count), colour="steelblue") + 
    #geom_text(data = nsf, aes(label = n.grads), vjust = 2, size = 2.75) +
    geom_point(data = articles.year.df, aes(as.factor(years), y = articles.year.df$year.count), colour="steelblue") + 
    annotate("text", factor(c(2002, 2005, 2008, 2012)), 
    c(165, 225, 250, 190) + 150, label = c("238","323", "338", "280") , size = 3) + 
    annotate("text", articles.x, articles.placement, label = articles.label, size=3)

sm.scopus.merged.3 <- sm.scopus.merged %>% group_by(Year) %>%
    mutate(HD.N = sum(N))

sm.scopus.merged.4 <- sm.scopus.merged %>% select(Year, Documents)

sm.scopus.merged.4 <- na.omit(sm.scopus.merged.4)
sm.scopus.merged.4 <- sm.scopus.merged.4 %>% group_by(Year) %>% mutate(scopus.N = sum(Documents))

ggplot(sm.scopus.merged.3, aes(Year, HD.N), group=1) + geom_line() +
    geom_line(data =sm.scopus.merged.4, aes(Year, scopus.N), colour = "red")

@@

```{r plotJournalCount, eval=TRUE}
n.journals.year <- filter(full.df, attributes == "journal") %>%
    select(articleID, record)

@@

```{r plotH-Index, eval=TRUE}
final.list.index <- within(final.list.index, quartile <- as.integer(cut(h5Index, quantile(h5Index, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))

final.list.index <- within(final.list.index, years <- as.numeric(last) - as.numeric(first) +1)

plotIndex <- ggplot(final.list.index, aes(x = n, y = h5Index )) + 
    geom_point(aes(colour=factor(quartile), size = years), alpha=.80) +
    geom_smooth() + 
    scale_colour_manual(values=cp)

@@

```{r authorNames}
authorNames  <- filter(full.df, attributes == "author")

authorNames.df <- authorNames
authorNames.df$record <- sub("(?<=, [A-Z]).*$", "", authorNames.df$record, perl=TRUE)
authorNames.df <- authorNames.df %>% group_by(record) %>% 
    summarize(N = n()) %>%
    arrange(desc(N))
```{r gade, eval=TRUE}
years <- c(1989:2015)
programs <- rep(NA, 27)
gade <- as.data.frame(cbind(as.character(years), programs))
gade$programs <- as.numeric(gade$programs)
gade[15, 2] <- 72
gade[27, 2] <- 86
colnames(gade) <- c("years", "programs")
```

@@

```{r ratios}
years <- c(1989:2013)
article.grad.ratio <- articles.year.df$year.count / nsf$n.grads

ratio.df <- data.frame(cbind(years, article.grad.ratio))
colnames(ratio.df) <- c("years", "ratio")
ratio.df <- ratio.df[-(1:13), ]

grad.ratio.df.melted <- reshape2::melt(ratio.df, id.vars="years")

ratio.plot <- ggplot(grad.ratio.df.melted, aes(years, value, group= variable, 
    color=variable)) + geom_line() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_continuous(breaks=c(seq(2002, 2013))) +
    scale_y_continuous(limits = c(0,8)) +
    ylab("Value") +
    xlab("Year")

```{r eval=FALSE}
colnames(n.journals.year) <- c("years", "journals")
n_authors2 <- rename(n_authors2, years = ID, Avg.Authors = Average, Mdn.Authors = Median, Sd.Authors = Standard_Deviation)

scholarly.df <- left_join(articles.year.df, n.journals.year, by = "years") 
scholarly.df <- left_join(scholarly.df, n_authors2, by = "years")
scholarly.df <- left_join(scholarly.df, nsf, by = "years")
scholarly.df <- left_join(scholarly.df, pages.df, by = "years")
scholarly.df[c(26, 27), ] <- rep(NA)
scholarly.df[26, 1] <- 2014
scholarly.df[27, 1] <- 2015

scholarly.df <- mutate(scholarly.df, years = as.numeric(years)) %>%
    rename(article.count = year.count, journal.count = year.count, program.growth = growth) 
scholarly.df$gade <- rep(NA, nrow(scholarly.df))  
scholarly.df$gade[15] <- 72
scholarly.df$gade[27] <- 86
```

>>>>

df.96.10 <- df.96.10 %>% mutate(countNotCited = HD.N * propNotCited)

@@

# We need to include years before and after the scopus data.

@@

uncited.df <- rbind(df.96.10.Summary, df.95.11) %>%
    arrange(Year)

#============================================
# Compute percentage variable and melt
#============================================

uncited.df$percentage <- uncited.df$Uncited/uncited.df$Published*100

uncited.melted <- reshape2::melt(uncited.df[,c("Year", "Published", "Uncited")], 
     id.vars = c("Year"))

@@

plotArticles <- ggplot(uncited.melted, aes(Year, value, colour = variable,)) + 
    geom_line(alpha = .60) + 
    geom_point(size = 4) +
    scale_color_manual(values=cp, labels = c("Number of Articles Published",
         "Estimated Number of Uncited Articles")) +
    theme(legend.title=element_blank()) +
    theme(legend.position = "bottom") +
    ylab("N") +
    geom_text(data = percent.df, aes(Year, Uncited -70, label = percentLabel), size =4, colour = "black") +
    scale_y_continuous(breaks = seq(0, 2250, 250), limits = c(0, 2250))

@@

```{r}
# Read Scopus database
scopus.df <- read.csv("scopus.csv")

boxplot.scopus <- ggplot(subset(scopus.df, subset =Year <=2013 & Year >= 1999), aes(as.factor(Year), IPP)) +
    geom_boxplot()

@@

```{r plotJournalCount, eval=TRUE}

n.journals.year <- filter(full.df, attributes == "journal") %>%
    select(articleID, record)

@@

@@

@@
